### 2020-05-25 writeup/setup.tex
sec 2

We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on the test error for the target task:
	\begin{align*}
		\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
		&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
	\end{align*}

We would like to get insight on how covariate and model shifts affect the rate of transfer.
We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.

@@

For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
\end{align}
where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.

>>>>

Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$.
Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d. entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
Without loss of generality, let the $t$-th task denote the target task.
For an estimator $\hat{\beta}\in\real^p$, the test error for target task is defined as
	\begin{align*}
		\te_t(\hat{\beta}) \define \exarg{z}{\exarg{\varepsilon_t}{({(\Sigma_t^{1/2} z)}^{\top}\hat{\beta} - {(\Sigma_t^{1/2})}^{\top}\beta_t)^2}}
		= \exarg{\varepsilon_t}{(\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)}.
	\end{align*}

Let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$ denote the linear regression estimator, which can be also be obtained from equation \eqref{eq_mtl} by using the target task alone.
The bias-variance trade-off \cite{HTF09} says that
	\[ \te_t(\hat{\beta}) =
		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}. \]
Recall that we assume $n_i > p$ for every $1\le i\le t$.
Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $\sigma^2 \cdot \tr{(X_i^{\top}X_i)^{-1}\Sigma_i}$.

For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
\end{align}
where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).

@@

It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
